Turbulence and Particle Acceleration in Giant Radio Halos: the Origin of Seed Electrons

### 2016-04-18 paper.tex
Update paper.tex

\section{Parameter space exploration with spherical models}
...
\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{Radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{Radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.aCR.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.aI0.eps}
   \end{center}
\end{minipage}
\caption{...}
  \label{fig:param_comp}
\end{figure*}

>>>>

\section{Parameter space exploration with spherical models}
...
\begin{figure*}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{Radio profiles}\\
     \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}\Large{Radio spectra}\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.Xtu.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aCR.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aCR.eps}
   \end{center}
\end{minipage}
\\
\begin{minipage}{1\columnwidth}
  \begin{center}%\Large{\Mflatturb:}\\ 
    \includegraphics[width=\columnwidth]{prof.comp.KrTTDth.aI0.eps}
  \end{center}
\end{minipage}
\begin{minipage}{1\columnwidth}
   \begin{center}%\Large{\it Brunetti et al. (2012)}:\\
     \includegraphics[width=\columnwidth]{spec.comp.KrTTDth.aI0.eps}
   \end{center}
\end{minipage}
\caption{...}
  \label{fig:param_comp}
\end{figure*}
